Covariate analysis of MSSM reprocessed counts (with TMM normalisation)

### 2017-03-08 code/Rmd/MSSM_RNASeq_Reprocessed_TMM_BinnedCDR.Rmd
Minor modifications

### Associate differential expression results with gc content and gene length
```{r associate.de}
geneLength.GCcontent = EDASeq::getGeneLengthAndGCContent(unique(DE1$ensembl_gene_id), 
                                                         org = 'hsa', 
                                                         mode = "biomart") %>%
  rownameToFirstColumn('ensembl_gene_id')

>>>>

### Associate differential expression results with gc content and gene length
```{r associate.de, eval = FALSE}
geneLength.GCcontent = EDASeq::getGeneLengthAndGCContent(unique(DE1$ensembl_gene_id), 
                                                         org = 'hsa', 
                                                         mode = "biomart") %>%
  rownameToFirstColumn('ensembl_gene_id')
